---
title: "R Programming Task 2"
output: html_notebook
---


#### 1. Object x <-1:15
Construct a 5x3 matrix for the value of x.

```{r}
x <- 1:15
matrix(x, nrow=5, ncol=3)
```

#### 2. Write a program to generate the following 4x4 matrix
0 0 0 0 
0 0 0 0 
0 0 0 0 

```{r}
matrix(0, nrow=4, ncol=4)
```

#### 3. The object x<-1:8
Write a program to generate the following 3x8 matrix using "cbind(),rbind(),rev(),rep()"

1 2 3 4 5 6 7 8
8 7 6 5 4 3 2 1
3 3 3 3 3 3 3 3

```{r}
x <- 1:8
rbind(unname(x), rev(x), rep(3, 8))
```

#### 4. Chose two different(x,y) 4x4 matrix to perform the following arithmetic operations
(a). x + y
(b). x - y 
(c). x*y 
(d). x%*%y 
(e). Difference between (c) &(d) 
(f). Inverse of y 
(g). z<-x/y 
(h). Transpose of z 
(i). Diagonal of transpose matrix

```{r}
x <- matrix(3:18, nrow=4)
y <- matrix(4:19, nrow=4)

"(a)"
x + y

"(b)"
x - y

"(c)"
x*y

"(d)"
x%*%y

"(e). (c) is element multiplication and (d) is matrix multiplication."

"(f)"
library(MASS)
ginv(y)

"(g)"
z <- x/y
z

"(h)"
transpose <- t(z)
transpose

"(i)"
diag(diag(transpose))
```


#### 5. Difference between (i) & (ii)
i. x<-matrix(x<-1:9,3,3,byrow = TRUE)
ii. x<-matrix(x<-1:9,3,3)

Answer:
(i) arranges the matrix row by row.
(ii) arranges the matrix column by column (default).

```{r}
x<-matrix(x<-1:9,3,3,byrow = TRUE)
x
x<-matrix(x<-1:9,3,3)
x
```


#### 6. Which function can we use for inner product and outer product in matrix calculation?
Answer:
- Inner product is used %*% in matrix calculation
- Outer product is used %o% in matrix calculation

Example:
```{r}
"Inner product result"
x <- 1:8
x%*%x

"Outer product result"
x <- 1:7
y <- 2:5
x %o% y
```

#### 7. Explain the use of all.equal() function in Matrix with a sample program.
Answer: all.equal() is used to compare 2 matrices to check if they are nearly equal/exactly equal or not. If two matrices is identical, it returns true. Otherwise, it returns mean relative difference if they are not identical.

Example:
```{r}
# equal = return true
x <- matrix(4:19, nrow=4)
y <- matrix(4:19, nrow=4)
all.equal(x,y)

# not equal = return mean relative difference
x <- matrix(3:18, nrow=4)
y <- matrix(4:19, nrow=4)
all.equal(x,y)
```

#### 8. Explain the use of dim() function with a sample program.
Answer: `dim()` function is used retrieve or set the dimension of an object. For matrices, `dim()` returns the number of rows and columns as an integer vector.It returns 2 integer numbers that the first one indicates number of row and second one indicates number of column.

Example:
```{r}
m <- matrix(1:12, nrow=2, ncol=4)
dim(m)
```


#### 9. Use of $ operator, and square brackets [] in List with example program.
Answer: $ or ( [[]] and [] ) is used to subset vector inside list.
- $ operator in List is used to access the element in the list by name.
- [[]] or [] square brackets operator in List is used to access the element in the list by index.

Example:
```{r}
lst <- list(name = "Mila", weight = 43, height = 159)

"access with $ operator"
lst$name
lst$weight
lst$height

"access with [] operator"
lst[1:3]
```

#### 10. Explain ifelse() with example.
Answer: `ifelse()` function is used for convert one variable to other variables based on logical expression or condition. It requires 3 parameter such as:

- the logical expression or condition
- the return value if the condition is true
- the return value if the condition is false

Example:
```{r}
x <- 1:9
ifelse(x %% 2 == 0, "even", "odd")
```

#### 11. Write a program to get the weight and height from the user to calculate the following cases
a. If your BMI is less than 18.5, it falls within the underweight range.
b. If your BMI is 18.5 to <25, it falls within the normal.
c. If your BMI is 25.0 to <30, it falls within the overweight range.
d. If your BMI is 30.0 or higher, it falls within the obese range.

```{r}
w <- as.integer(readline(prompt="Enter your weight in kg: "))
h <- as.numeric(readline(prompt="Enter your height in m: "))
bmi <- w/h^2

if(bmi<18.5){
    "Underweight Range"
}else if (bmi<25) {
    "Normal Range"
}else if (bmi<30) {
    "Overweight Range"
}else{
    "Obese Range"
}
```


#### 12. Difference between List and Data frame with an example program.
Answer:
- List is the array of element of same or different type that store in sequence.
- Data Frame is the matrix of the same or different type that store in the form of row and column.

```{r}
# List
list(name = "Mila", weight = 43, height = 159)

# Data frame
w <- c( 56,67,87,68)
h <- c( 158,159,160,169)
data.frame(Weight = w, Height = h)
```


### 13. Difference between repeat and while loop with example program.
Answer:
- Repeat is the loop that doesn't take condition but we need to call `break` to exit the loop.
- for/While is the loop that take a condition to run the loop and determine when to finish looping.

```{r}
"Repeat loop"
i <- 1
repeat {
  if (i==3) break;
  print(i);
  i<-i+1
  }

"While Loop"
i <- 3
while (i!=7) {
  print(i);
  i<-i+1
  }
```




